Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-03-30 paper_latex_edit - Copy.tex
Reviewer 1- Comment 1 Authors have not addressed anything related to MIMO architecture

Like most scenarios adopts a single cell massive MIMO system, in which the base station equips
\begin{math}\ N_{t}\end{math} transmitting antennas as well as the UE with a single
receiving antennas. An orthogonal frequency division multiplexing (OFDM) system with \begin{math}\ N_{c}\end{math} sub-carriers for FDD downlink massive MIMO is examined. In the OFDM-MIMO system considered in this work, the subcarriers are assumed to maintain orthogonality. We will assume on  \begin{math}  {n^{th}} \end{math} sub-carriers the received signal at UE will be equal to :

>>>>

Like most scenarios adopts a single user massive MIMO system in a single cell, in which the base station equips
\begin{math} N_{t} > 1\end{math} transmitting antennas as well as the UE with a single
receiving antennas. An orthogonal frequency division multiplexing (OFDM) system with \begin{math}\ N_{c}\end{math} sub-carriers for FDD downlink massive MIMO is examined. In the OFDM-MIMO system considered in this work, the subcarriers are assumed to maintain orthogonality. We will assume on  \begin{math}  {n^{th}} \end{math} sub-carriers the received signal at UE will be equal to :
